Untitled

### 2023-09-05 code/analysis_Redo.Rmd
playing with the pre-post filters on treatment effect estimates

df.core <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100,

>>>>

df.core <- dfc %>% 
  #filter(Att %in% c(0, 2016:2021) & Year %in% c(2014:2021)) %>% 
  #filter(Att %in% c(0, 2012:2015) & Year %in% c(2010:2018)) %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100,
